The \dealii{} Library, Version 8.4.0

### 2016-03-01 8.4/deal84.tex
Move 8.4 files to their own directory.
More funding

>>>>

G.~Kanschat and M.~Kronbichler were partially supported by the German Research
Foundation (DFG) through the project ExaDG. M.~Kronbichler also acknowledges
the Gauss Centre for Supercomputing e.V.~for funding algorithm enhancements by
providing computing time on the GCS Supercomputer SuperMUC at Leibniz
Supercomputing Centre (LRZ) through project id \emph{pr83te}.
